Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-03-01 paper.Rmd
minor edits

---
title: "Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists"
author:
  - name: Ronald M. Visser
    orcid_id: 0000-0001-6966-1729
    role: 
      - Writing - Original Draft Preparation
      - Formal Analysis
      - Visualization
      - Writing - Review & Editing
    affiliation: Saxion University of Applied Sciences
  - name: Annemarie Jutte
    orcid_id: 0000
    role: 
    - Writing - Original Draft Preparation
    - Writing - Review & Editing
    affiliation: Saxion University of Applied Sciences
  - name: Doug Rocks-Macqueen 
    orcid_id: 0000
    role: 
      - Software
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    affiliation: Landward Research Teoranta
  - name: Iza Romanowska 
    orcid_id: 00000
    role: 
     - Writing - Original Draft Preparation
     - Writing - Review & Editing
    affiliation: Aarhus University
  - name: Tom Brughmans
    role: 
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    orcid_id: 0000
    affiliation: Aarhus University
  - name: Laura van der Knaap 
    role: 
      - Software
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    orcid_id: 0000
    affiliation: Leiden University
  - name: Karsten Lambers 
    role: 
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    orcid_id: 0000
    affiliation: Leiden University
  - name: Kenneth Aitchison 
    role: 
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
      - Project administration
    orcid_id: 0000
    affiliation: Landward Research Teoranta
  - name: Adam Pažout
    role: 
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    orcid_id: 0000
    affiliation: Aarhus University
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  distill::distill_article:
    number_sections: yes
    fig_caption: yes
  bookdown::pdf_document2:
    number_sections: yes
    keep_tex: true
    fig_caption: yes
  bookdown::word_document2:
    number_sections: yes
    fig_caption: yes
bibliography: references.bib
csl: journal-of-computer-applications-in-archaeology.csl
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
---

@@

>>>>

---
title: "Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists"
author:
  - name: Ronald M. Visser
    orcid_id: 0000-0001-6966-1729
    role: 
      - Writing - Original Draft Preparation
      - Formal Analysis
      - Visualization
      - Writing - Review & Editing
    affiliation: Saxion University of Applied Sciences
  - name: Annemarie Jutte
    orcid_id: 0000
    role: 
    - Writing - Original Draft Preparation
    - Writing - Review & Editing
    affiliation: Saxion University of Applied Sciences
  - name: Doug Rocks-Macqueen 
    orcid_id: 0000
    role: 
      - Software
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    affiliation: Landward Research Teoranta
  - name: Iza Romanowska 
    orcid_id: 0000-0002-9487-2111
    role: 
     - Writing - Original Draft Preparation
     - Writing - Review & Editing
    affiliation: Aarhus University
  - name: Tom Brughmans
    role: 
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    orcid_id: 0000
    affiliation: Aarhus University
  - name: Laura van der Knaap 
    role: 
      - Software
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    orcid_id: 0000
    affiliation: Leiden University
  - name: Karsten Lambers 
    role: 
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    orcid_id: 0000
    affiliation: Leiden University
  - name: Kenneth Aitchison 
    role: 
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
      - Project administration
    orcid_id: 0000
    affiliation: Landward Research Teoranta
  - name: Adam Pažout
    role: 
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
    orcid_id: 0000
    affiliation: Aarhus University
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  distill::distill_article:
    number_sections: yes
    fig_caption: yes
  bookdown::pdf_document2:
    number_sections: yes
    keep_tex: true
    fig_caption: yes
  bookdown::word_document2:
    number_sections: yes
    fig_caption: yes
bibliography: references.bib
csl: journal-of-computer-applications-in-archaeology.csl
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
---

@@

This project was funded as an Erasmus+ project (<https://erasmus-plus.ec.europa.eu/nl/projects/search/details/2021-2-IE01-KA220-VET-000049054>) and we thank the Erasmus+ program for enabling us to make these tutorials.
